\documentclass{itkmitlproject}

\usepackage{afterpage}
\usepackage{graphicx,amsmath,latexsym,amssymb,amsthm}
\usepackage{indentfirst}
\usepackage{cite}
\usepackage{placeins}
\usepackage[super,square]{natbib}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{hyphenat}

\setmainfont{Angsana}[
 Path = fonts/,
 UprightFont = Angsana,
 ItalicFont = *-Italic,
 BoldFont = *-Bold,
 BoldItalicFont = *-BoldItalic,
    Extension = .ttf,
    WordSpace = 0.9,
    Scale = 1.6
]

\graphicspath{ {images/} }

\makeatletter
% \patchcmd{<cmd>}{<search>}{<replace>}{<succes>}{<failure>}
\patchcmd{\@chapter}{\addtocontents{lof}{\protect\addvspace{10\p@}}}{}{}{}% LoF
\patchcmd{\@chapter}{\addtocontents{lot}{\protect\addvspace{10\p@}}}{}{}{}% LoT
\def\bibindent{2.1em}
\let\old@biblabel\@biblabel
\def\@biblabel#1{\old@biblabel{#1}\kern\bibindent}
\let\old@bibitem\bibitem
\def\bibitem#1{\old@bibitem{#1}\leavevmode\kern-\bibindent}
\makeatother

%1. Your thesis title (THAI)
\newcommand{\ThesisTitle}{ฟังก์ชันสูญเสียสำหรับการเรียนรู้ข้อมูลที่ไม่สมดุลของแบบจำลองโครงข่ายประสาทเทียมเชิงลึก}
%2. Your thesis title (ENG)
\newcommand{\ThesisTitleENG}{Hybrid Loss for Learning Imbalanced Data}
%3. Author name
\newcommand{\Author}{ธนวัฒน์ หลอดแก้ว}
%4. Author name ENG
\newcommand{\AuthorENG}{Thanawat Lodkaew}
%5. Author student ID
\newcommand{\SId}{59070071}
%9. Advisor name
\newcommand{\Advisor}{รองศาสตราจารย์ ดร. กิติ์สุชาต  พสุภา}
%10. Advisor name ENG
\newcommand{\AdvisorENG}{Assoc. Prof. Dr. Kitsucart  Pasupa}
%11. ภาคเรียนที่
\newcommand{\Sem}{1}
%12. ปีการศึกษา พ.ศ.
\newcommand{\AcaY}{2562}
%13. ปีการศึกษา ค.ศ.
\newcommand{\AcaYAD}{2019}
%14. วันส่งรายงาน
\newcommand{\SubD}{10 พฤศจิกายน พ.ศ. 2561}

\begin{document}    
    \frontmatter
    \lhead{}\rhead{}\chead{}\lfoot{}\cfoot{\thepage}\rfoot{}
    \makecover    
    \makeinnercover
    \makeengcover
    \makecopyrightcover
    \makethesiscert
    \makeprojectcert
   
    % Setting margin for page numbering on frontmatter
    \newgeometry{top=1in, bottom=1in, left=1.5in, right=1in, includefoot}
    
    \makeabstract{
        ปัญหาความไม่สมดุลของข้อมูลเป็นเรื่องที่ถูกหยิบขึ้นมาศึกษาอย่างแพร่หลาย  แบบจำลองโครงข่ายประสาทเทียมเชิงลึกสามารถให้ผลการทำงานที่ย่ำแย่เมื่อมันเรียนรู้จากชุดข้อมูลที่ไม่สมดุลกัน งานวิจัยนี้ได้นำเสนอฟังก์ชันสูญเสียแบบผสมผสานที่จะช่วยให้แบบจำลองสามารถเรียนรู้ข้อมูลที่ไม่สมดุลอย่างมีประสิทธิภาพ
        ฟังก์ชันสูญเสียนี้เป็นการผสมผสานกันระหว่างแนวคิดการคำนวณค่าสูญเสียของสองฟังก์ชันสูญเสีย ที่ซึ่งทั้งสองฟังก์ชันเป็นฟังก์ชันสูญเสียที่ถูกออกแบบมาเพื่อจัดการกับปัญหาความไม่สมดุลของข้อมูลอยู่แล้ว และมีแนวคิดการแก้ปัญหาที่ต่างกันและน่าสนใจ ผู้วิจัยจึงได้เสนอที่จะรวมแนวคิดของทั้งสองฟังก์ชันดังกล่าวเข้าด้วยกัน เพื่อที่จะทำให้ประสิทธิภาพของการเรียนรู้ของแบบจำลองนั้นดีขึ้น ฟังก์สูญเสียแบบผสมผสานที่นำเสนอถูกทดสอบกับชุดข้อมูลที่หลากหลาย และผลการทดลองแสดงให้เห็นว่าฟังก์ชันสูญเสียที่นำเสนอสามารถเพิ่มประสิทธิภาพของแบบจำลองได้เหนือกว่าฟังก์ชันสูญเสียอื่น ๆ 
    }

    \makeabstracteng{
        Classification of imbalanced data is extremely common in practice, and this problem has been widely studied in classical machine learning. 
        A deep neural network (DNN) model produced from an imbalanced data set is likely to be biased towards the majority class and show inferior classification accuracy on the minority class. 
        This work aims at inventing a new loss for learning imbalanced data. This loss is hybridized by two well-performed loss functions, mean false error (MFE) and focal loss (FL). The two loss functions are designed to combat the imbalance problem, and each of them has its own advantage. Hence, we propose to hybridize the two losses and redefine as a hybrid loss that applies the calculation procedures of MFE’s total loss to the focal loss. The proposed loss function is tested with several imbalanced datasets, and our experimental results show that it can overcome the existing loss functions.
    }

    \makeack

    \newpage
    \addcontentsline{toc}{chapter}{สารบัญ}
    \tableofcontents
    
    \newpage
    \addcontentsline{toc}{chapter}{สารบัญตาราง}
    \listoftables    
    
    \newpage
    \addcontentsline{toc}{chapter}{สารบัญภาพ}
    \listoffigures
    
    % Reset frontmatter page numbering margin, back to original margin from class file
    \restoregeometry

    \mainmatter
    \lhead{}\rhead{\thepage}\chead{}\lfoot{}\cfoot{}\rfoot{}
    
    \include{chapter1}
    \include{chapter2}
    \include{chapter3}
   	\include{chapter4}
   	\include{chapter5}
    
    \clearpage
    \addcontentsline{toc}{chapter}{บรรณานุกรม}
    \bibliographystyle{IEEEtran}
    \bibliography{reference}
    
    \startappendix
    \include{appendix}
    
\end{document}